### 2015-01-11 paper/Content/sources.tex
Minor stuff in solution chapter
Aktuelle Gartner Zahl

\bibitem{GartnerAndroid2014}
Gartner: \emph{Gartner Says Worldwide Traditional PC, Tablet, Ultramobile and 
Mobile Phone Shipments Are On Pace to Grow 6.9 Percent in 2014}, March 2014, 
[Online]. http://www.gartner.com/newsroom/id/2692318 (retrieved 02-Dec-2014)

@@

\bibitem{Fowler04}
M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,
[Online]. http://martinfowler.com/articles/injection.html (retrieved 10-Jan-2015)

>>>>

\bibitem{GartnerAndroid2015}
Gartner: \emph{Gartner Says Tablet Sales Continue to Be Slow in 2015}, January 2015, 
[Online]. http://www.gartner.com/newsroom/id/2954317 (retrieved 11-Jan-2015)

@@

\bibitem{FowlerIoC}
M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,
[Online]. http://martinfowler.com/articles/injection.html (retrieved 10-Jan-2015)
